Distributions

### 2021-12-28 Ch2_distributions/Ch2_Figures.Rmd
Table2

On average, how many units away is the second model from the best one?

```{r}
cp.bic %>% 
  filter(., deltaBIC != 0) %>% 
  group_by(boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  summary()
```

**PP** 
```{r}
pp.bic %>% 
  filter(., deltaBIC != 0) %>% 
  group_by(boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  summary()
```

**NP**
```{r}
np.bic %>% 
  filter(., deltaBIC != 0) %>% 
  group_by(boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  summary()
```

>>>>

# Table 2 - Average BIC units from best model

Table 2 - Mean and median distance for second best model in BIC units, for each of the pooling scenarios.

```{r Table2}
# cp.bic %>% 
#   filter(., deltaBIC != 0) %>% 
#   group_by(boot) %>% 
#   summarise(min = min(deltaBIC)) %>% 
#   summary()
# 
# pp.bic %>% 
#   filter(., deltaBIC != 0) %>% 
#   group_by(boot) %>% 
#   summarise(min = min(deltaBIC)) %>% 
#   summary()
# 
# np.bic %>% 
#   filter(., deltaBIC != 0) %>% 
#   group_by(boot) %>% 
#   summarise(min = min(deltaBIC)) %>% 
#   summary()

cp.bic %>% 
  bind_rows(pp.bic) %>% 
  bind_rows(np.bic) %>% 
  filter(., deltaBIC != 0) %>% 
  group_by(model, boot) %>% 
  summarise(min = min(deltaBIC)) %>% 
  group_by(model) %>% 
  summarise(median = median(min),
            mean = mean(min))
